Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-17 slides/presentation.tex
bug fixes

\begin{figure}
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[xmin=-2.5,xmax=2.5,ymin=-2,ymax=2]
\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
\node at (axis cs:.7,-.7) [pin={-10:{stable region}},inner sep=0pt] {};
\draw[color=blue] (axis cs:0.5,0.7) ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

@@

\textcolor{red}{Copy here CEGIS architecture scheme.}

@@

   \& complexnode/.pic={ 
      \only<1-2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
      \only<3>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.75cm]dac.center) {};}
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2cm,yshift=.5cm]plant.center)  {\sc \only<1-2>{$\mat{B}$}\only<3>{$\mat{B}_d$}};
      \node[draw=none] (u) at ([xshift=-.8cm,yshift=.15cm]B)  {\only<1-2>{$u(t)$}};
      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-0.6cm,yshift=.5cm]plant.center) {};
      \node[draw=none] (xdot) at ([xshift=.9cm,yshift=.2cm]p1)  {\only<1-2>{$\dot{\mat{x}}(t)$}\only<3>{$\mat{x}_{k+1}$}};   
      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=1.2cm,yshift=.5cm]plant.center) {\sc \only<1-2>{$\int$}\only<3>{$Z^{-1}$}};
      \coordinate (xsouth) at ([xshift=1cm]int);
      \node[draw=none] (x) at ([xshift=1.2cm,yshift=.15cm]int)  {\only<1-2>{$\mat{x}(t)$}\only<3>{$\mat{x}_k$}};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=1.2cm,yshift=-1cm]plant.center)  {\sc \only<1-2>{$\mat{A}$}\only<3>{$\mat{A}_d$}};
      \coordinate (aeast) at ([xshift=1cm]A);
      \coordinate (awest) at ([xshift=-1.8cm]A);
    }

>>>>

\begin{figure}
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[xmin=-2.5,xmax=2.5,ymin=-2,ymax=2]
\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
\node at (axis cs:.5,-.866) [pin={-80:{stable region}},inner sep=0pt] {};
\draw[color=blue] (axis cs:0.5,0.7) ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

@@

\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };

   \path (verif2) edge node {} (done);
   \path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);
   \path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
   \path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);
   \path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);
   \path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);
   \path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);
   \path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);
   \path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);
   \path (aux1) edge (synth.north);
   \path[-] (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2);
   \path[-] ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
 \end{tikzpicture}
}
\end{figure}

@@

   \& complexnode/.pic={ 
      \only<1>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.4cm]dac.center) {};}
      \only<2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
      \only<3>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.75cm]dac.center) {};}
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2cm,yshift=.5cm]plant.center)  {\sc \only<1-2>{$\mat{B}$}\only<3>{$\mat{B}_d$}};
      \node[draw=none] (u) at ([xshift=-.8cm,yshift=.15cm]B)  {\only<1-2>{$u(t)$}};
      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-0.6cm,yshift=.5cm]plant.center) {};
      \node[draw=none] (xdot) at ([xshift=.9cm,yshift=.2cm]p1)  {\only<1-2>{$\dot{\mat{x}}(t)$}\only<3>{$\mat{x}_{k+1}$}};   
      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=1.2cm,yshift=.5cm]plant.center) {\sc \only<1-2>{$\int$}\only<3>{$Z^{-1}$}};
      \coordinate (xsouth) at ([xshift=1cm]int);
      \node[draw=none] (x) at ([xshift=1.2cm,yshift=.15cm]int)  {\only<1-2>{$\mat{x}(t)$}\only<3>{$\mat{x}_k$}};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=1.2cm,yshift=-1cm]plant.center)  {\sc \only<1-2>{$\mat{A}$}\only<3>{$\mat{A}_d$}};
      \coordinate (aeast) at ([xshift=1cm]A);
      \coordinate (awest) at ([xshift=-1.8cm]A);
    }
